Advantages of mixed quantum gates for information processing

### 2019-03-19 decorrelation/mixed_unitaries.tex
removing reference to run time of any particular quadratic optimization problem

\begin{equation}\label{eq:robust_minimization}
  \begin{split}
    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}\omega||\\
    &\textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=\vec{0}\\
  \end{split}
\end{equation}
with $D_n^j$ defined in Equation \ref{eq:taylor}. The time to solve these convex optimization problems is independent of the number of rows, which in our case is the number of drifting parameters. However, the size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the runtime of solving the optimization problem grows as $N^4$, with $d$ being the number of drifting parameters, and $N$ being the number of controls.\needcite

>>>>

\begin{equation}\label{eq:robust_minimization}
  \begin{split}
    &\underset{\omega_j\geq0, |\omega|_1=1}{\textbf{minimize}: } ||{\bold{D}^{\ell}}\omega||\\
    &\textbf{subject to: } \forall n<\ell, \sum \omega_jD_j^n=\vec{0}\\
  \end{split}
\end{equation}
with $D_n^j$ defined in Equation \ref{eq:taylor}. The size of the matrix that must be computed before solving grows as $Nd^{\ell}$, and the time required to solve the optimization problem will depend on the particular optimizer and algorithm used.
